Classless Java

### 2015-11-03 paper/sections/RelatedWork.tex
related work (in progress)

\section{Related Work}\label{sec:related}

Multiple Inheritance in Java

default methods and the paper that we found. 
traits programming in java 8.
- proposals for extending Java with traits/multiple inheritance/...

Multiple Inheritance

- traits (original, variations, scala)
- mixins (original, scala)
- multiple inheritance
- ...

ThisType/MyType/Extensibility

@@

Type-Directed Translations/Syntactic Sugar

@@

- Meta-programming techniques?

@@

Fluent Interfaces

>>>>

\section{Related Work}\label{sec:related}
In this section we discuss related work and comparison to Classless Java.

\subsection{Multiple Inheritance in Java}
Since Java 8 default methods are introduced, which enables concrete method
implementation to be defined (via the \textbf{default} keyword) inside
interface. Since in Java supports extension on multiple interfaces (instead of
classes), the introduction of default methods opens the gate of doing multiple
inheritance in Java by using interfaces. Details on achieving multiple
inheritance by mimicking trait programing through interfaces are summarized by
Bono.et. al.~\cite{bono14}. There is also formalization proposed by
Goetz and Field~\cite{goetz12fdefenders} to formalize defender (default) methods
in Java. However this formalization is limited since they only model exactly one
method inside classes/interfaces, where in our formalization multiple methods
may be defined.

There are proposals for extending Java with traits. For example, FeatherTrait
Java (FTJ)~\cite{Liquori08ftj} by Liquori et al. extends the calculus of
Featherweight Java (FJ)~\cite{Igarashi01FJ} with statically-typed traits, adding
trait-based inheritance in Java. \yanlin{Drawbacks to be added...}

\paragraph{Multiple Inheritance}
Traits~\cite{} and mixins~\cite{} provides novel models of new programming
architecture in object oriented programming paradim. As shown in
section~\ref{sec:comparison}, although they solved some multiple inheritance
problems, they are extremely restricting expressiveness.

- traits (original, variations, scala)
- mixins (original, scala)
- c++ solution : virtual inheritance
- multiple inheritance
- ...

\paragraph{ThisType/MyType/Extensibility}

@@

\paragraph{Type-Directed Translations/Syntactic Sugar}

@@

\paragraph{Meta-programming techniques}
- MetaFJig*

@@

\paragraph{Fluent Interfaces}
